### 2024-04-19 docs/SOSP 2024/motivation.tex
Edit motivation figure

\begin{figure*}[]
  \begin{subfigure}[t]{.495\linewidth}
    \vspace{0pt}
    \centering
    \includegraphics[width=\linewidth]{figures/MotivatingExample1.PNG}
    \caption{\label{fig:schedulea}}
  \end{subfigure}\hfill
  \begin{subfigure}[t]{.495\linewidth}
    \vspace{0pt}
    \centering
    \includegraphics[width=\linewidth]{figures/MotivatingExample2.PNG}
    \caption{\label{fig:scheduleb}}
  \end{subfigure}
  \caption{Some possible schedules to compile the motivating example and the generated \Treebeard{} IR.}
  \label{Fig:Schedules}
\end{figure*}

@@

These \Treebeard{} schedules just use a combination of 4-8 constructs and already generate strategies 
that are different from what library based systems like XGBoost, Tahoe and RAPIDs FIL use. 
As one can imagine, several other schedules with different trade-offs can be generating using 
these constructs.

>>>>

\begin{figure*}[]
  \begin{subfigure}[t]{.5\linewidth}
    \vspace{0pt}
    \centering
    \includegraphics[width=\linewidth]{figures/MotivatingExample1.PNG}
    \caption{\label{fig:schedulea}}
  \end{subfigure}\hfill
  \begin{subfigure}[t]{.5\linewidth}
    \vspace{0pt}
    \centering
    \includegraphics[width=\linewidth]{figures/MotivatingExample2.PNG}
    \caption{\label{fig:scheduleb}}
  \end{subfigure}
  \caption{Some possible schedules to compile the motivating example and the generated \Treebeard{} IR.
  The arrows connect entities in the schedule to related entities in the IR. }
  \label{Fig:Schedules}
\end{figure*}

@@

These \Treebeard{} schedules just use a combination of 4-8 constructs and already generate strategies 
that are different from what library based systems like XGBoost, Tahoe and RAPIDs FIL use. 
As one can imagine, several other schedules with different trade-offs can be generated using 
these constructs.
